Informing policy via dynamic models: Cholera in Haiti

### 2024-01-16 r1/response.tex

\report{
  6. Please add uncertainty intervals to the estimated parameters in Table 1. If necessary, consider splitting the table into two or including this additional information in the supplementary material. I suggest this update because there is an indication of unidentifiability when parameter estimates are fairly broad.
}

\report{
  7. In line 159, it is stated that ``$\upsilon^\star(t)$ is efficacy at time $t$ since vaccination for adults" and then ``single and double vaccine doses were modeled by changing the waning of protection; protection was modeled as equal between single and double dose until 52 weeks after vaccination, at which point the single dose becomes ineffective". I examined the reference from which this function is based but found only a numeric table. Please provide the equation of this function or a detailed description in the supplementary information. It would be beneficial for readers to understand how to model this complex feature.
}

\report{
  8. Lines 209-211. In model 2, an incidence measurement is employed to configure a prevalence compartment. As the authors may know, initial values severely condition the dynamics of a model. Please explain this decision. Is it because that was the approach followed in the original formulation (Lee at al's paper)?
}

Our starting point was the formulation of \cite{lee20}.
Judging by the referee's comment, they will not be suprised to learn that this structure led to difficulties in some situations. \TODO{}

@@

\report{
  9. Lines 245-247. Same comment as before. What’s the justification for assuming incidence measurements as the basis for prevalence states? What are the risks?
}

The cholera pathogen was recently introduced to Haiti, which facilitates the specification of initial conditions.
The goals of inferring initial prevalence is to reduce the number of parameters.
The risk is that the form of this assumption could have substantial effects on the dynamics, and hence on the consequences of the analysis.
Our approaches to addressing this issue involve: (i) looking at residual diagnostic plots to assess time points at which the model is misspecified; (ii) if the initial values seem problematic, calculate the room for improvement by estimating the initial values as free parameters.

@@

\report{
  10. Line 262. ``deterministic Model 2 is a degenerate case of a stochastic model". Please explain why or provide a reference.
}

\report{
  11. Lines 260-274. Please add more citations.
}

\report{
  12. Lines 343-345. This sentence is key for this paper, but it’s hard to follow: ``The robust statistical conclusion is that a model which allows for change fits better than one which does not—we argue that a decreasing transmission rate is a plausible way to explain this, but the incidence data themselves do not provide enough information to pin down the mechanism". Please rephrase.
}

This is similar to point 11 of referee 1. LET'S DISCUSS THIS. Our point is that there are many other ways one might include time-varying effects in the model, and a strongly supported conclusion should avoid ruling out untested hypotheses.  We can say that the best available model with trending parameters is statistically superior to the best available model with time-constant parameters. This frames the evidence in a way that avoids asserting clear support for any one particular way of modeling this effect.

R1 mentioned the possibility of reporting rate decreasing instead. I'M TRYING TO RECALL OUR REASONING THAT MODEL 3 IN LEE ET AL OVER-EMPHASIZED THIS. APART FROM THE POSSIBILITY OF A CASE DEFINITION CHANGE, ONE MIGHT EXPECT REPORTING RATE TO INCREASE?

@@

\report{
  13. Line 357. ``Determining the necessary computational effort needed to maximize model likelihoods and acting accordingly" How do we determine the necessary computational effort?
}

\report{
  14. Please add the predicted intervals to Fig 4. I would like to see the effect of the log-normal measurement model.
}

\report{
  15. Lines 513-515. Please clarify the comparison between disaggregated models and a benchmark. Let’s say I have spatial units 1 and 2, for which I have observations y1 and y2. Should I fit the disaggregated mechanistic model to y1 and y2 simultaneously (as usual) but keep a record of the individual log-likelihoods (log-lik y1 and log-lik y2). In parallel, fit the benchmark independently to y1 and y2, and then compare by log-likelihoods or information criteria by spatial unit.
}

The benchmarks we have looked at operate independently on each unit, and in this case the joint log-likelihood benchmark for units 1 and 2 is the sum of the marginal log-likelihoods.
A simple statistical benchmark does not need to have this structure; for example, one could consider an autoregressive model including spatial dependence.

In general, a joint model for units 1 and 2 may not have well-defined individual log-likelihoods log-lik y1 and log-lik y2 that sum to the full likelihood.
An exception arises in the case of likelihood evaluation by the block particle filter, in which conditinal log likelihoods for each block of units do sum to the total log likelihood estimate.
If the block approximation is found to be appropriate \cite{ionides21,ionides22} then fits can be compared against an independent benchmark for each block, and then summed to compare on the entire dataset.

Since the value of benchmarks is a major point in this paper, we have added these extra details in a supplementary section \TODO{}.

### 2024-01-16 ms.Rnw
Temporarily changed bake calls to "readRDS". Also fixed a few citation bugs.
pomp version: 5.5
spatPomp version: 0.34.1
haitipkg version: 3.0.0.9002 (the updates to the package shouldn't matter removing the bake calls)
R Version: 4.2.3

# Compute the run_level_<RUN_LEVEL> results and save them.
lee_epi_ll <- bake(
  file = paste0("model1/", rl_dir, "lee1_epi_evals.rds"), {

    # Randomly sample from starting params used by Lee et al (2020).
    # If RUN_LEVEL == 3, all starting parameters are used.
    which_params <- sample(
      1:nrow(h1LeeStartsEpi),
      size = N_PARAMS,
      replace = FALSE
    )
    epi_params <- h1LeeStartsEpi[which_params, ]

    # Create data.frame to save results
    lee_epi_ll <- data.frame(
      "pfLL" = NA_real_,
      "pfse" = NA_real_,
      "parid" = epi_params$parid
    )

    for (j in 1:nrow(lee_epi_ll)) {
      # Get parameters of interest
      pf_params <- epi_params[j, -1][names(coef(h1_epi))]

      # make results reproducible
      registerDoRNG((j * 687383921) %% 7919)

      # Calculate log likelihoods
      ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
        logLik(pfilter(h1_epi, params = pf_params, Np = NP_EVAL))
      }
      lee_epi_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]  # Log-lik
      lee_epi_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]  # SE
    }

    lee_epi_ll
  }
)

@@

lee_end_ll <- bake(
  file = paste0("model1/", rl_dir, "lee1_end_evals.rds"), {

    end_params <- h1LeeStartsEnd[h1LeeStartsEnd$parid %in% lee_epi_ll$parid, ]

    # Create data.frame to save results
    lee_end_ll <- data.frame(
      "pfLL" = NA_real_,
      "pfse" = NA_real_,
      'parid' = end_params$parid
    )

    # Perform particle filter to get likelihood estimates
    for (j in 1:nrow(lee_end_ll)) {
      # Get parameters of interest
      pf_params <- end_params[j, ][names(coef(h1_end))]

      # make results reproducible
      registerDoRNG((j * 687383921) %% 7919)

      # Calculate log likelihoods
      ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
        logLik(pfilter(h1_end, params = pf_params, Np = NP_EVAL))
      }

      lee_end_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]
      lee_end_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]
    }

    lee_end_ll
  }
)

@@

This case study investigates the use of dynamic models and spatiotemporal data to inform public health policy in the context of the cholera outbreak in Haiti, which started in 2010.
Various dynamic models were developed to study this outbreak: searching PubMed with keywords ``Haiti, cholera, model'' we obtained 20 deterministic models \cite{kirpich16,kirpich17,andrews11,botelho21,fitzgibbon20,eisenberg13,rinaldo12,chao11,date11,lin19,collins21,akman15,trevisin22,mavian20,collins14,kelly16,capone14,bengtsson15,mari15,gatto12} and 8 stochastic models \cite{tuite11,mukandvire13,lewnard16,kunke17,sallah17,azman12,kuhn14,azman15}.
Here we focus on a multi-group modeling exercise by Lee et al.~\cite{lee20} in which four expert modeling teams developed models to the same dataset with the goal of comparing conclusions on the feasibility of eliminating cholera by a vaccination campaign.
Model~1 is stochastic and describes cholera at the national level;
Model~2 is deterministic with spatial structure, and includes transmission via contaminated water;
Model~3 is stochastic with spatial structure, and accounts for measured rainfall.
Model~4 has an agent-based construction, featuring considerable mechanistic detail but limited ability to calibrate these details to data.
These modeling strategies were selected by \cite{li20} to represent the range of approaches used in the research community.
We focus on Models~1--3, as the strengths and weaknesses of the agent-based modeling approach \cite{tracy18} are outside the scope of this article.
\eic{In addition, agent-based models were less widely used [NO OTHERS SHOW UP IN OUR LITERATURE REVIEW???].}
The data that were used for this study, and that is the subject of our reanalysis, are displayed in Fig.~\ref{fig:CholeraData}.

@@

# Create the <RUN_LEVEL> version of the results and save them.
h1_MIF <- bake(
  file = paste0("model1/", rl_dir, "haiti1_fit.rds"), {
    fit_haiti1(  # haitipkg function used to fit Model 1
      NP = NP_H1,
      NMIF = NMIF_H1,
      NUM_TREND = NUM_TREND,
      NPROF = NPROF,
      NREPS_EVAL = NREPS_EVAL,
      NP_EVAL = NP_EVAL
    )
  }
)

@@

h2_fit <- bake(
  file = paste0("model2/model2_fit.rds"), {
    fit_haiti2()
  },
  timing = FALSE
)
@

@@

# Fit Model 3
haiti3_fit <- bake(
  file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
    fit_haiti3(
      nsearches = 2L,
      search1 = SEARCH1,
      search2 = SEARCH2,
      search_rho = FALSE,
      search_gamma = FALSE,
      search_Iinit = TRUE,
      search_hur = TRUE
    )
  }
)

@@

# Calculate likelihood via block-particle filter
mod3_eval_res <- bake(
  file = paste0('model3/', rl_dir, 'mod3_eval_res.rds'), {

    # Create a list to store results
    results <- list()

    coef(h3Spat) <- p3

    # Perform block-particle filter
    h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
      bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
    }

    ll <- logLik(h3_bpf)
    results$ll <- logmeanexp(ll[!is.na(ll)], se = FALSE)

    ### Get likelihood for subset of the data

    # Find appropriate sub-set
    in_subset_cols <- h3_bpf[[1]]@times >= as.numeric(lubridate::decimal_date(as.Date("2014-03-01")))
    in_subset_rows <- h3_bpf[[1]]@unit_names != 'Ouest'

    mod3_coupled_subset_evals <- c()
    for (i in 1:length(h3_bpf)) {
      mod3_coupled_subset_evals <- c(
        mod3_coupled_subset_evals,
        sum(h3_bpf[[i]]@block.cond.loglik[in_subset_rows, in_subset_cols])
      )
    }

    results$subset_ll <- logmeanexp(mod3_coupled_subset_evals)
    results
  },
  timing = FALSE
)

@@

lee3_results <- bake(
  file = paste0('model3/', rl_dir, 'lee3_results.rds'), {

    # Create lists to save results
    lee3_results <- list()

    # Save how long it takes for sub-data
    lee3_results[["sub_bpf_time"]] <- system.time({

      lee3_sub_ll_evals <- foreach(
        i = 1:lee3_NREP, .combine = rbind
      ) %dopar% {

        liks <- numeric(10L)

        lee_bpf_out <- bpfilter(lee3_sub, block_size = 1, Np = lee3_NP)
        Ouest_ind <- which(lee_bpf_out@unit_names == "Ouest")

        for (u in 1:10) {
          if (u == Ouest_ind) {
            liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, lee3_sub@times >= lubridate::decimal_date(as.Date('2017-06-10'))])
          } else {
            liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, ])
          }
        }

        liks
      }
    })

    # Save all likelihood evaluations
    lee3_results[["sub_ll_eval"]] <- logmeanexp(rowSums(lee3_sub_ll_evals)[!is.na(rowSums(lee3_sub_ll_evals))])

    registerDoRNG(2789131)

    # Save how long it takes for all data
    lee3_results[["all_pf_time"]] <- system.time({
      # Save all likelihood evaluations

      lee3_all_ll_evals <- foreach(
        i = 1:lee3_NREP, .combine = c
      ) %dopar% {
        logLik(bpfilter(lee3_all, block_size = 1, Np = lee3_NP))  # Get likelihood evaluations
      }

      lee3_results[["all_ll_eval"]] <- logmeanexp(lee3_all_ll_evals[!is.na(lee3_all_ll_evals)])

    })

    lee3_results[["n_params"]] <- 29

    lee3_results
  },
  timing = FALSE
)

@@

# Run Vaccination scenarios for Model 2. Note that the code runs the same
# speed for each run-level.
mod2_VaccScenarios <- bake(
  file = paste0("model2/VaccinationScenarios.rds"), {
    haiti2_vaccScenario(
      h2_params = h2_fit$h2_params
    )
  },
  timing = FALSE
)
@

@@

# Get quantiles of simulations from the calibrated Model 3.
h3_quants <- bake(
  file = paste0('model3/', rl_dir, 'h3Sims.rds'), {

    coef(h3Spat) <- p3
    # Simulate from the fitted version of Model 3
    h3_sims <- simulate(
      h3Spat, nsim = h3_nsim, format = 'data.frame'
    )

    # For each department and time-point, calculate percentiles of the
    # simulations
    h3_sims %>%
      rename(dep = unitname) %>%
      group_by(dep, time) %>%
      summarise(
        q05 = quantile(cases, 0.025, na.rm = T),
        mean = mean(cases, na.rm = T),
        q50 = quantile(cases, 0.5, na.rm = T),
        q95 = quantile(cases, 0.975, na.rm = T)
      ) %>%
      ungroup() %>%
      mutate(
        date = lubridate::date_decimal(time)
      ) %>%
      mutate(date = as.Date(lubridate::round_date(date, unit = 'day')))
  },
  timing = FALSE
)

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S0_results <- bake(
  file = paste0("model1/", rl_dir, "S0_sims.rds"), {

    # Create the model
    s0 <- haiti1_joint(vacscen = 'id0')

    # Load coefficients
    coef(s0) <- p1

    # Get samples from filtering distribution
    s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s0_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S0_sims <- project_from_filter(mod = s0, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
    results$mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S2_results <- bake(
  file = paste0('model1/', rl_dir, 'S2_sims.rds'), {

    # Create the model
    s2 <- haiti1_joint(vacscen = "id2")

    # Set model parameters that need to be adjusted
    depts <- 2
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s2) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s2_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
    results$mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S4_results <- bake(
  file = paste0('model1/', rl_dir, 'S4_sims.rds'), {

    # Create the model
    s4 <- haiti1_joint(vacscen = "id4")

    # Set model parameters that need to be adjusted
    depts <- 3
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s4) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s4_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
    results$mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)

    results
  },
  timing = FALSE
)

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S3_results <- bake(
  file = paste0('model1/', rl_dir, 'S3_sims.rds'), {

    # Create the model
    s3 <- haiti1_joint(vacscen = "id3")

    # Set model parameters that need to be adjusted
    depts <- 10
    h1_par_names <- names(p1)
    h1_params_temp <- c(p1, rep(0.0, 5 * depts))
    names(h1_params_temp) <- c(
      h1_par_names,
      paste0("S", 1:depts, "_0"),
      paste0("E", 1:depts, "_0"),
      paste0("I", 1:depts, "_0"),
      paste0("A", 1:depts, "_0"),
      paste0("R", 1:depts, "_0")
    )
    coef(s3) <- h1_params_temp  # Set model parameters

    # Get samples from filtering distribution for Scenario 2 model:
    s3_pf <- pfilter(s3, save.state = TRUE, Np = h1_scen_NP)
    end_states <- saved_states(s3_pf)
    end_states <- end_states[[length(end_states)]]

    # project vacc scenario, with filtering dist, and model.
    h1_S3_sims <- project_from_filter(mod = s3, end_states = end_states, nsims = h1_scen_sims)

    results <- list()
    results$mod1_V3_sims <- agg_mod1_sims(h1_S3_sims)
    results$mod1_V3_probs <- get_elimProbs(h1_S3_sims, model = 1)

    results
  },
  timing = FALSE
)

>>>>

# Compute the run_level_<RUN_LEVEL> results and save them.
lee_epi_ll <- readRDS("model1/run_level_3/lee1_epi_evals.rds")
# lee_epi_ll <- bake(
#   file = paste0("model1/", rl_dir, "lee1_epi_evals.rds"), {
#
#     # Randomly sample from starting params used by Lee et al (2020).
#     # If RUN_LEVEL == 3, all starting parameters are used.
#     which_params <- sample(
#       1:nrow(h1LeeStartsEpi),
#       size = N_PARAMS,
#       replace = FALSE
#     )
#     epi_params <- h1LeeStartsEpi[which_params, ]
#
#     # Create data.frame to save results
#     lee_epi_ll <- data.frame(
#       "pfLL" = NA_real_,
#       "pfse" = NA_real_,
#       "parid" = epi_params$parid
#     )
#
#     for (j in 1:nrow(lee_epi_ll)) {
#       # Get parameters of interest
#       pf_params <- epi_params[j, -1][names(coef(h1_epi))]
#
#       # make results reproducible
#       registerDoRNG((j * 687383921) %% 7919)
#
#       # Calculate log likelihoods
#       ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
#         logLik(pfilter(h1_epi, params = pf_params, Np = NP_EVAL))
#       }
#       lee_epi_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]  # Log-lik
#       lee_epi_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]  # SE
#     }
#
#     lee_epi_ll
#   }
# )

@@

lee_end_ll <- readRDS("model1/run_level_3/lee1_end_evals.rds")
# lee_end_ll <- bake(
#   file = paste0("model1/", rl_dir, "lee1_end_evals.rds"), {
#
#     end_params <- h1LeeStartsEnd[h1LeeStartsEnd$parid %in% lee_epi_ll$parid, ]
#
#     # Create data.frame to save results
#     lee_end_ll <- data.frame(
#       "pfLL" = NA_real_,
#       "pfse" = NA_real_,
#       'parid' = end_params$parid
#     )
#
#     # Perform particle filter to get likelihood estimates
#     for (j in 1:nrow(lee_end_ll)) {
#       # Get parameters of interest
#       pf_params <- end_params[j, ][names(coef(h1_end))]
#
#       # make results reproducible
#       registerDoRNG((j * 687383921) %% 7919)
#
#       # Calculate log likelihoods
#       ll_evals <- foreach(i=1:NREPS_EVAL, .combine = c) %dopar% {
#         logLik(pfilter(h1_end, params = pf_params, Np = NP_EVAL))
#       }
#
#       lee_end_ll[j, 'pfLL'] <- logmeanexp(ll_evals, se = TRUE)[1]
#       lee_end_ll[j, 'pfse'] <- logmeanexp(ll_evals, se = TRUE)[2]
#     }
#
#     lee_end_ll
#   }
# )

@@

This case study investigates the use of dynamic models and spatiotemporal data to inform public health policy in the context of the cholera outbreak in Haiti, which started in 2010.
Various dynamic models were developed to study this outbreak: searching PubMed with keywords ``Haiti, cholera, model'' we obtained 20 deterministic models \cite{kirpich16,kirpich17,andrews11,botelho21,fitzgibbon20,eisenberg13,rinaldo12,chao11,date11,lin19,collins21,akman15,trevisin22,mavian20,collins14,kelly16,capone15,bengtsson15,mari15,gatto12} and 8 stochastic models \cite{tuite11,mukandavire13,lewnard16,kunkel17,sallah17,azman12,kuhn14,azman15}.
Here we focus on a multi-group modeling exercise by Lee et al.~\cite{lee20} in which four expert modeling teams developed models to the same dataset with the goal of comparing conclusions on the feasibility of eliminating cholera by a vaccination campaign.
Model~1 is stochastic and describes cholera at the national level;
Model~2 is deterministic with spatial structure, and includes transmission via contaminated water;
Model~3 is stochastic with spatial structure, and accounts for measured rainfall.
Model~4 has an agent-based construction, featuring considerable mechanistic detail but limited ability to calibrate these details to data.
These modeling strategies were selected by \cite{li20} to represent the range of approaches used in the research community.
We focus on Models~1--3, as the strengths and weaknesses of the agent-based modeling approach \cite{tracy18} are outside the scope of this article.
\eic{In addition, agent-based models were less widely used [NO OTHERS SHOW UP IN OUR LITERATURE REVIEW???].}
The data that were used for this study, and that is the subject of our reanalysis, are displayed in Fig.~\ref{fig:CholeraData}.

@@

# Create the <RUN_LEVEL> version of the results and save them.
h1_MIF <- readRDS('model1/run_level_3/haiti1_fit.rds')

# h1_MIF <- bake(
#   file = paste0("model1/", rl_dir, "haiti1_fit.rds"), {
#     fit_haiti1(  # haitipkg function used to fit Model 1
#       NP = NP_H1,
#       NMIF = NMIF_H1,
#       NUM_TREND = NUM_TREND,
#       NPROF = NPROF,
#       NREPS_EVAL = NREPS_EVAL,
#       NP_EVAL = NP_EVAL
#     )
#   }
# )

@@

h2_fit <- readRDS("model2/model2_fit.rds")

# h2_fit <- bake(
#   file = paste0("model2/model2_fit.rds"), {
#     fit_haiti2()
#   },
#   timing = FALSE
# )
@

@@

# Fit Model 3
haiti3_fit <- readRDS("model3/run_level_3/haiti3_fit.rds")
# haiti3_fit <- bake(
#   file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
#     fit_haiti3(
#       nsearches = 2L,
#       search1 = SEARCH1,
#       search2 = SEARCH2,
#       search_rho = FALSE,
#       search_gamma = FALSE,
#       search_Iinit = TRUE,
#       search_hur = TRUE
#     )
#   }
# )

@@

# Calculate likelihood via block-particle filter
mod3_eval_res <- readRDS("model3/run_level_3/mod3_eval_res.rds")
# mod3_eval_res <- bake(
#   file = paste0('model3/', rl_dir, 'mod3_eval_res.rds'), {
#
#     # Create a list to store results
#     results <- list()
#
#     coef(h3Spat) <- p3
#
#     # Perform block-particle filter
#     h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
#       bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
#     }
#
#     ll <- logLik(h3_bpf)
#     results$ll <- logmeanexp(ll[!is.na(ll)], se = FALSE)
#
#     ### Get likelihood for subset of the data
#
#     # Find appropriate sub-set
#     in_subset_cols <- h3_bpf[[1]]@times >= as.numeric(lubridate::decimal_date(as.Date("2014-03-01")))
#     in_subset_rows <- h3_bpf[[1]]@unit_names != 'Ouest'
#
#     mod3_coupled_subset_evals <- c()
#     for (i in 1:length(h3_bpf)) {
#       mod3_coupled_subset_evals <- c(
#         mod3_coupled_subset_evals,
#         sum(h3_bpf[[i]]@block.cond.loglik[in_subset_rows, in_subset_cols])
#       )
#     }
#
#     results$subset_ll <- logmeanexp(mod3_coupled_subset_evals)
#     results
#   },
#   timing = FALSE
# )

@@

lee3_results <- readRDS("model3/run_level_3/lee3_results.rds")
# lee3_results <- bake(
#   file = paste0('model3/', rl_dir, 'lee3_results.rds'), {
#
#     # Create lists to save results
#     lee3_results <- list()
#
#     # Save how long it takes for sub-data
#     lee3_results[["sub_bpf_time"]] <- system.time({
#
#       lee3_sub_ll_evals <- foreach(
#         i = 1:lee3_NREP, .combine = rbind
#       ) %dopar% {
#
#         liks <- numeric(10L)
#
#         lee_bpf_out <- bpfilter(lee3_sub, block_size = 1, Np = lee3_NP)
#         Ouest_ind <- which(lee_bpf_out@unit_names == "Ouest")
#
#         for (u in 1:10) {
#           if (u == Ouest_ind) {
#             liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, lee3_sub@times >= lubridate::decimal_date(as.Date('2017-06-10'))])
#           } else {
#             liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, ])
#           }
#         }
#
#         liks
#       }
#     })
#
#     # Save all likelihood evaluations
#     lee3_results[["sub_ll_eval"]] <- logmeanexp(rowSums(lee3_sub_ll_evals)[!is.na(rowSums(lee3_sub_ll_evals))])
#
#     registerDoRNG(2789131)
#
#     # Save how long it takes for all data
#     lee3_results[["all_pf_time"]] <- system.time({
#       # Save all likelihood evaluations
#
#       lee3_all_ll_evals <- foreach(
#         i = 1:lee3_NREP, .combine = c
#       ) %dopar% {
#         logLik(bpfilter(lee3_all, block_size = 1, Np = lee3_NP))  # Get likelihood evaluations
#       }
#
#       lee3_results[["all_ll_eval"]] <- logmeanexp(lee3_all_ll_evals[!is.na(lee3_all_ll_evals)])
#
#     })
#
#     lee3_results[["n_params"]] <- 29
#
#     lee3_results
#   },
#   timing = FALSE
# )

@@

# Run Vaccination scenarios for Model 2. Note that the code runs the same
# speed for each run-level.
mod2_VaccScenarios <- readRDS("model2/VaccinationScenarios.rds")
# mod2_VaccScenarios <- bake(
#   file = paste0("model2/VaccinationScenarios.rds"), {
#     haiti2_vaccScenario(
#       h2_params = h2_fit$h2_params
#     )
#   },
#   timing = FALSE
# )
@

@@

# Get quantiles of simulations from the calibrated Model 3.
h3_quants <- readRDS("model3/run_level_3/h3Sims.rds")
# h3_quants <- bake(
#   file = paste0('model3/', rl_dir, 'h3Sims.rds'), {
#
#     coef(h3Spat) <- p3
#     # Simulate from the fitted version of Model 3
#     h3_sims <- simulate(
#       h3Spat, nsim = h3_nsim, format = 'data.frame'
#     )
#
#     # For each department and time-point, calculate percentiles of the
#     # simulations
#     h3_sims %>%
#       rename(dep = unitname) %>%
#       group_by(dep, time) %>%
#       summarise(
#         q05 = quantile(cases, 0.025, na.rm = T),
#         mean = mean(cases, na.rm = T),
#         q50 = quantile(cases, 0.5, na.rm = T),
#         q95 = quantile(cases, 0.975, na.rm = T)
#       ) %>%
#       ungroup() %>%
#       mutate(
#         date = lubridate::date_decimal(time)
#       ) %>%
#       mutate(date = as.Date(lubridate::round_date(date, unit = 'day')))
#   },
#   timing = FALSE
# )

@@

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S0_results <- readRDS("model1/run_level_3/S0_sims.rds")
# h1_S0_results <- bake(
#   file = paste0("model1/", rl_dir, "S0_sims.rds"), {
#
#     # Create the model
#     s0 <- haiti1_joint(vacscen = 'id0')
#
#     # Load coefficients
#     coef(s0) <- p1
#
#     # Get samples from filtering distribution
#     s0_pf <- pfilter(s0, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s0_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S0_sims <- project_from_filter(mod = s0, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V0_sims <- agg_mod1_sims(h1_S0_sims)
#     results$mod1_V0_probs <- get_elimProbs(h1_S0_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S2_results <- readRDS("model1/run_level_3/S2_sims.rds")
# h1_S2_results <- bake(
#   file = paste0('model1/', rl_dir, 'S2_sims.rds'), {
#
#     # Create the model
#     s2 <- haiti1_joint(vacscen = "id2")
#
#     # Set model parameters that need to be adjusted
#     depts <- 2
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s2) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s2_pf <- pfilter(s2, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s2_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S2_sims <- project_from_filter(mod = s2, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V1_sims <- agg_mod1_sims(h1_S2_sims)
#     results$mod1_V1_probs <- get_elimProbs(h1_S2_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )

# Simulate vaccination scenario from filtering distribution. The code
# below creates a model, samples from the filtering distribution, and then
# projects the vaccination scenario, under the specified model.
h1_S4_results <- readRDS("model1/run_level_3/S4_sims.rds")
# h1_S4_results <- bake(
#   file = paste0('model1/', rl_dir, 'S4_sims.rds'), {
#
#     # Create the model
#     s4 <- haiti1_joint(vacscen = "id4")
#
#     # Set model parameters that need to be adjusted
#     depts <- 3
#     h1_par_names <- names(p1)
#     h1_params_temp <- c(p1, rep(0.0, 5 * depts))
#     names(h1_params_temp) <- c(
#       h1_par_names,
#       paste0("S", 1:depts, "_0"),
#       paste0("E", 1:depts, "_0"),
#       paste0("I", 1:depts, "_0"),
#       paste0("A", 1:depts, "_0"),
#       paste0("R", 1:depts, "_0")
#     )
#     coef(s4) <- h1_params_temp  # Set model parameters
#
#     # Get samples from filtering distribution for Scenario 2 model:
#     s4_pf <- pfilter(s4, save.state = TRUE, Np = h1_scen_NP)
#     end_states <- saved_states(s4_pf)
#     end_states <- end_states[[length(end_states)]]
#
#     # project vacc scenario, with filtering dist, and model.
#     h1_S4_sims <- project_from_filter(mod = s4, end_states = end_states, nsims = h1_scen_sims)
#
#     results <- list()
#     results$mod1_V2_sims <- agg_mod1_sims(h1_S4_sims)
#     results$mod1_V2_probs <- get_elimProbs(h1_S4_sims, model = 1)
#
#     results
#   },
#   timing = FALSE
# )
